\section{Methodology}
\subsection{System Modelling}
\paragraph{}The predictive maintenance algorithm for motors system  will be obtained from governing equations from which a transfer function will be generated from the linearized model. The transfer function will be used to generate a state space model for the system. 
\paragraph{}

The observed sources of faults and their relative frequency. Such sources can be the core components of the machine or its various sensors (such accelerometers and flow meters).

The process measurements through sensors. The number, type and location of sensors, and their reliability and redundancies all will create both algorithm and comparative model.

The sources of faults will  translate to observed symptoms. Such cause-effect analysis will require extensive processing of data from the available sensors.

Physical knowledge about the system dynamics.will result in mathematical modeling of the system and its faults and from the insights of data. Understanding system dynamics will involve detailed knowledge of relationships among various signals from the machinery (such as input-output relationships among the actuators and sensors), the machine operating range, and the nature of the measurements (for example, periodic, constant or stochastic).

The ultimate maintenance goal, such as fault recovery or development of a maintenance schedule.


\subsection{Simulations}
\paragraph{}From the generated models on matlab, simulations will be performed using the different controllers and the responses and other metrics will be plotted out for further analysis. Metrics such as rise time, settling time and stochastic response will be observed to determine the system performance.
\subsection{Sensors}
\paragraph{}Sensors will be used to collect data from the system as it runs. These include:
\begin{itemize}
\item Humidity sensor
\item Temperature sensor
\item Flow rate sensor
\item Pressure sensors
\item Voltage sensor
\item Current sensor
\end{itemize}
\paragraph{}These sensors will be used by the controller to observe system performance and optimize for each parameter as well as the performance requirements.
\subsection{Data Analysis}
\paragraph{}The data collected from the simulations and sensors will be analysed using custom software created using jupyter notebooks. Graphs will  be generated to compare the performance of each controller and evaluation of the selected controller.